lme-r

### 2024-10-28 code/analysis/06-lme-with-R.qmd
models-trend

# Set the country
country <- 'Mexico'

@@

@@

@@

df$Of <- factor(df$O)
df$Df <- factor(df$D)
eq4 <- y ~ time + (time|Of) + (time|Df)
m4 <- glmmTMB(eq4, data = df)
m4_re <- plot_model(m4, type ="re")
summary(m4)

eq5 <- y ~ time + time2 + (time|O) + (time|D)
m5 <- glmmTMB(eq5, data = df)
m5_re <- plot_model(m5, type ="re")
summary(m5)

@@

```{r}
m4_re[[1]]$data
m4_re[[2]]$data
m5_re[[2]]$data
m5_re[[2]]$data
m4_re
m5_re
```

```{r}
p1_m1me <- plot_model(m, terms = c("1", "time")) %>% 
  .$data %>% ggplot(aes(x=estimate, y=term, color=group)) +
  geom_point(size = 3.5,  colour = "black") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), 
                width=.05, color= "black") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_color_manual(values=c("#88ccee")) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10.5)
  ) +
  scale_y_discrete(labels=c("time" = "Week", 
                            "1" = "Intercept")) +
  geom_vline(xintercept=0, 
             linetype="solid", 
             color = "grey20",
             linewidth=1,
             alpha =.2) +
  labs(title = "Main fixed effects")

@@

```{r}
eq <- y ~  time + (time | O) + (time | D)
model <- glmmTMB(eq, data = df)
```

```{r}
summary(model)
```

```{r}
p1_m <- plot_model(model, terms = c("time", "O", "D")) %>% 
  .$df %>% ggplot(aes(x=estimate, y=term, color=group)) +
  geom_point(size = 3.5,  colour = "black") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), 
                width=.05, color= "black") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_color_manual(values=c("#88ccee")) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10.5)
  ) +
  scale_y_discrete(labels=c("z_stringency_index" = "Stringency t", 
                            "z_cases" = "New cases t",
                            "lag(z_stringency_index, 1)" = "Stringency t-1")) +
  geom_vline(xintercept=0, 
             linetype="solid", 
             color = "grey20",
             linewidth=1,
             alpha =.2) +
  labs(title = "c",
       subtitle = " Main fixed effects")

@@

```{r}
coef_model <- coef(model)
head(coef_model$O)
```

```{r}
ranef_model <- ranef(model)
head(ranef_model$O)
```

```{r}
# obtain estimates
merTools::REsim(model) %>% head(10)
```

```{r}
plotREsim(REsim(model)) 
```

```{r}
## regression table
tab_model(mode, 
          collapse.ci = TRUE,
          p.style = "stars",
          show.aic = TRUE,
          #terms = c(), # show selected coefficients
          #rm.terms = c("time [1st degree]"), #remove selected coefficients
          #pred.labels = c("Intercept", "Stringency t", "New Cases t", "Stringency t-1",
          #                "Spline 1st degree", "Spline 2nd degree", 
          #                "Spline 3rd degree", "New cases t-1"),
          #dv.labels = c("Autoregressive", "Stringency random effects", "New COVID-19 cases random effects"),
          #file = "../outputs/modelling/estimates/reg_table.txt"
)
```

>>>>

# Set the country
country <- 'Argentina'

@@

###

@@

eq2o <- y ~ time + O
m2o <- glmmTMB(eq2o, data = df)
summary(m2o)

###

@@

eq3o <- y ~ time + (1|O)
m3o <- glmmTMB(eq3o, data = df)
m3o_re <- plot_model(m3o, type ="re")
summary(m3o)

###

df$Of <- factor(df$O)
df$Df <- factor(df$D)
eq4 <- y ~ time + (0 + time|Of) + (0 + time|Df)
m4 <- glmmTMB(eq4, data = df)
m4_re <- plot_model(m4, type ="re")
summary(m4)

df$Of <- factor(df$O)
eq4o <- y ~ time + (0 + time|Of) 
m4o <- glmmTMB(eq4o, data = df)
m4o_re <- plot_model(m4o, type ="re")
summary(m4o)

###

df$Of <- factor(df$O)
df$Df <- factor(df$D)
eq5 <- y ~ time + (time|Of) + (time|Df)
m5 <- glmmTMB(eq5, data = df)
m5_re <- plot_model(m5, type ="re")
summary(m5)

df$Of <- factor(df$O)
eq5o <- y ~ time + (time|Of) 
m5o <- glmmTMB(eq5o, data = df)
m5o_re <- plot_model(m5o, type ="re")
summary(m5o)

###

eq6 <- y ~ time + time2 + (time|O) + (time|D)
m6 <- glmmTMB(eq6, data = df)
m6_re <- plot_model(m6, type ="re")
summary(m6)

@@

```{r}
m3o$fit$par
m4o$fit$par
m5o$fit$par
m3o_re
m4o_re
m5o_re
```

file_m3o <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m3o.csv')
write.csv(m3o$fit$par, file_m3o, row.names = FALSE)

file_m3o_re <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m3o_re.csv')
write.csv(m3o_re[[1]], file_m3o_re, row.names = FALSE)

###

file_m4o <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m4o.csv')
write.csv(m4o$fit$par, file_m4o, row.names = FALSE)

file_m4o_re <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m4o_re.csv')
write.csv(m4o_re[[1]], file_m4o_re, row.names = FALSE)

###

file_m5o <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m5o.csv')
write.csv(m5o$fit$par, file_m5o, row.names = FALSE)

file_m5o_re <- paste0(wd, '/data/outputs/', country_short, '/mov-analysis/by-', category, '/data_trend_param_m5o_re.csv')
write.csv(m5o_re[[1]], file_m5o_re, row.names = FALSE)

```{r}
p1_m1me <- plot_model(m3o_re, terms = c("1", "time")) %>% 
  .$data %>% ggplot(aes(x=estimate, y=term, color=group)) +
  geom_point(size = 3.5,  colour = "black") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), 
                width=.05, color= "black") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_color_manual(values=c("#88ccee")) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10.5)
  ) +
  scale_y_discrete(labels=c("time" = "Week", 
                            "1" = "Intercept")) +
  geom_vline(xintercept=0, 
             linetype="solid", 
             color = "grey20",
             linewidth=1,
             alpha =.2) +
  labs(title = "Main fixed effects")

@@

```{r}
eq <- y ~  time + (time | O) + (time | D)
model <- glmmTMB(eq, data = df)
```
`

```{r}
pm3o <- plot_model(m3o, terms = c("time", "O")) %>% 
  .$df %>% ggplot(aes(x=estimate, y=term, color=group)) +
  geom_point(size = 3.5,  colour = "black") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), 
                width=.05, color= "black") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_color_manual(values=c("#88ccee")) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10.5)
  ) +
  scale_y_discrete(labels=c("z_stringency_index" = "Stringency t", 
                            "z_cases" = "New cases t",
                            "lag(z_stringency_index, 1)" = "Stringency t-1")) +
  geom_vline(xintercept=0, 
             linetype="solid", 
             color = "grey20",
             linewidth=1,
             alpha =.2) +
  labs(title = "c",
       subtitle = " Main fixed effects")

@@
